---
title: "Simple document"
output: github_document
---

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(haven)
```

## Import data

I want to import 'FAS_litters.csv'

```{r}
litters_df = read_csv("data/FAS_litters.csv")

```

I imported the dataset. Now I want better names

```{r}
names(litters_df)

litters_df = janitor::clean_names(litters_df)
```

Here's skimr

```{R}
skimr::skim(litters_df)
```

## Arguments in 'read_csv'

```{R}
litters_df = read_csv("data/FAS_litters.csv",
                      skip = 5,
                      col_names = F,
                      na = "low8")
```

## Parsing columns

```{R}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
tail(litters_data)
``` 

## Reading fron excel

REading mlb data

```{R}
mlb11_df = read_excel("data/mlb11.xlsx")
```

LotR words is next

```{R}
fellow_df = read_excel("data/LotR_Words.xlsx", range = "B3:D6")
```

## Read SAS file

Try to read sas file but failed

```{R}
#pulse_df = read_sas("data/public_pulse_data.sas7bdat")
```

## why not read.csv

'read.csv' does not give 'tibble' and that is bad

## how do i export data

there is a good way!

```{R}
write_csv(fellow_df, "data/fellowship_words.csv")
```

```{R}

```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.